Differential invariant signatures for planar Lie group transformations of images

### 2017-06-16 paper/paper.tex
Updates

\documentclass{article}
\usepackage{amsmath, amsthm, amssymb, mathtools}
\newtheorem{theorem}{Theorem}

@@

\subsection{Technical wank}
Completeness, degeneracy, moving frames as concept, table of numbers of
derivatives, all that jazz, maybe scaling technique
for dealing with invariants of non-unit weight

@@

>>>>

\documentclass{article}
\usepackage{amsmath, amsthm, amssymb, mathtools}
\usepackage{graphicx}
\newtheorem{theorem}{Theorem}

@@

\subsection{Technical wank}
Completeness, degeneracy, moving frames as concept table of numbers of
derivatives, all that jazz, maybe scaling technique
for dealing with invariants of non-unit weight

@@

\begin{figure}
	\includegraphics[width=12cm]{../images/SE2Transform_signature}
	\caption{SE(2) signature}
\end{figure}
\begin{figure}
	\includegraphics[width=12cm]{../images/E2Transform_signature}
	\caption{E(2) signature}
\end{figure}
\begin{figure}
	\includegraphics[width=12cm]{../images/SA2Transform_signature}
	\caption{SA(2) signature}
\end{figure}
\begin{figure}
	\includegraphics[width=12cm]{../images/A2Transform_signature}
	\caption{A(2) signature}
\end{figure}
